Preparación de datos

### 2022-06-22 production/prod_analysis-fix-t5.Rmd
modelos dummy educacion y 3-way-interac

```{r, results='asis',fig.dim=c(10,6)}
rm(list=ls())
if (!require("pacman")) install.packages("pacman") # instalar pacman
                            # cargar librerias
pacman::p_load(dplyr,       # Manipulacion de datos
               knitr,
               kableExtra,
               summarytools,
               lme4,
               texreg,
               sjPlot
               )
load(file = here::here("input/data-proc/df_study_t5_ind_comunas.RData"))

# generate analytical sample
df_study1 <- 
  df_study_long_t5_comunas %>%
  select(idencuesta,ola,comuna,cuestion_mig,
         in_ansied,in_simpat,in_valfam,in_valami,in_amigcl,
         in_simili,in_amsimb,in_acpier,in_acadop,
         conviviality, identity,
         in_amreal,educ,quintil1:edad,
         inm_prop_cas17_w,inm_prop_cas20_w,dif_inm) %>% 
  na.omit() %>% 
  mutate(
    # conviviality=(in_ansied+in_simpat+in_valfam+in_valami+in_amigcl)/5,
         # identity= (in_simili+in_amsimb+in_acpier+in_acadop)/4,
         ola_f = ola,
         ola=as.numeric(ola),
         -in_amreal
         )

# Hypothesis___________________________________________________________________
h1.cat <- "ola_f+educ+quintil1+ess+know_inm_t1t4+frien_inm_t1t4+pos_id+edad+inm_prop_cas20_w+dif_inm+nation_t1+cuestion_mig"
h1 <- "ola+educ+quintil1+ess+know_inm_t1t4+frien_inm_t1t4+pos_id+edad+inm_prop_cas20_w+dif_inm+nation_t1+cuestion_mig"
h2.educ <- "ola*educ+quintil1+ess+know_inm_t1t4+frien_inm_t1t4+pos_id+edad+inm_prop_cas20_w+dif_inm+nation_t1+cuestion_mig"
h2.incom <- "ola+educ+quintil1*ola+ess+know_inm_t1t4+frien_inm_t1t4+pos_id+edad+inm_prop_cas20_w+dif_inm+nation_t1+cuestion_mig"
h3 <- "ola*dif_inm+educ+quintil1+ess+know_inm_t1t4+frien_inm_t1t4+pos_id+edad+inm_prop_cas20_w+dif_inm+nation_t1+cuestion_mig"
h4.know <- "ola+dif_inm+educ+quintil1+ess+know_inm_t1t4*ola+frien_inm_t1t4+pos_id+edad+inm_prop_cas20_w+dif_inm+nation_t1+cuestion_mig"
h4.friend <- "ola+dif_inm+educ+quintil1+ess+know_inm_t1t4+frien_inm_t1t4*ola+pos_id+edad+inm_prop_cas20_w+dif_inm+nation_t1+cuestion_mig"

hipotesis <- c(h1.cat,h1,h2.educ,h2.incom,h3,h4.know,h4.friend)
# Set the independent variables (IVs)
ivs<- df_study1 %>% select(starts_with("in_"),"conviviality","identity") %>% names()

@@

# Tables_______________________________________________________________________
omit <- "(pos_id)|(edad)|(cuestion_mig)|(nation_t1)|(quintil1QNA)|(Intercept)"
reorderc <- c(1:4,19,5:18,20:31) # the depends on the number of coeficients (!)
# detail for subsections:
# https://stackoverflow.com/questions/69338331/r-markdown-create-section-headers-in-r-and-print-r-output-in-same-section

@@

knitreg(l = fit1[names(fit1)[grepl("in_ansied", names(fit1))]],
        omit.coef = omit,reorder.coef = reorderc)

cat(paste0("\n## ","B. Simpathy ","\n"))

@@

cat(paste0("\n## ","Conviviality (average)","\n"))

knitreg(l = fit1[names(fit1)[grepl("conviviality", names(fit1),"\n")]],
        omit.coef = omit,reorder.coef = reorderc)

@@

knitreg(l = fit1[names(fit1)[grepl("in_acadop", names(fit1))]],
        omit.coef = omit,reorder.coef = reorderc)

cat(paste0("\n## ","Identity (average)","\n"))

>>>>

## Education categorical {-}
```{r average-educ, results='asis',fig.dim=c(10,6)}
rm(list=ls())
if (!require("pacman")) install.packages("pacman") # instalar pacman
                            # cargar librerias
pacman::p_load(dplyr,       # Manipulacion de datos
               knitr,
               kableExtra,
               summarytools,
               lme4,
               texreg,
               sjPlot,
               ggplot2
               )
load(file = here::here("input/data-proc/df_study_t5_ind_comunas.RData"))

old <- theme_set(theme_bw());theme_set(old)
theme_replace(legend.position="bottom")

# generate analytical sample
df_study1 <- 
  df_study_long_t5_comunas %>%
  select(idencuesta,ola,comuna,cuestion_mig,
         in_ansied,in_simpat,in_valfam,in_valami,in_amigcl,
         in_simili,in_amsimb,in_acpier,in_acadop,
         conviviality, identity,
         in_amreal,educ,quintil1:edad,
         inm_prop_cas17_w,inm_prop_cas20_w,dif_inm) %>% 
  na.omit() %>% 
  mutate(
    # conviviality=(in_ansied+in_simpat+in_valfam+in_valami+in_amigcl)/5,
         # identity= (in_simili+in_amsimb+in_acpier+in_acadop)/4,
         ola_f = ola,
         ola=as.numeric(ola),
         primary = car::recode(educ,recodes = "'Primary'=1;else=0",as.factor = T),
         -in_amreal
         )

# Hypothesis___________________________________________________________________
h1.cat <- "ola_f+educ+quintil1+ess+know_inm_t1t4+frien_inm_t1t4+pos_id+edad+inm_prop_cas20_w+dif_inm+nation_t1+cuestion_mig"
h1 <- "ola+educ+quintil1+ess+know_inm_t1t4+frien_inm_t1t4+pos_id+edad+inm_prop_cas20_w+dif_inm+nation_t1+cuestion_mig"
h2.educ <- "ola*educ+quintil1+ess+know_inm_t1t4+frien_inm_t1t4+pos_id+edad+inm_prop_cas20_w+dif_inm+nation_t1+cuestion_mig"
h2.incom <- "ola+educ+quintil1*ola+ess+know_inm_t1t4+frien_inm_t1t4+pos_id+edad+inm_prop_cas20_w+dif_inm+nation_t1+cuestion_mig"
h3 <- "ola*dif_inm+educ+quintil1+ess+know_inm_t1t4+frien_inm_t1t4+pos_id+edad+inm_prop_cas20_w+dif_inm+nation_t1+cuestion_mig"
h4.know <- "ola+dif_inm+educ+quintil1+ess+know_inm_t1t4*ola+frien_inm_t1t4+pos_id+edad+inm_prop_cas20_w+dif_inm+nation_t1+cuestion_mig"
h4.friend <- "ola+dif_inm+educ+quintil1+ess+know_inm_t1t4+frien_inm_t1t4*ola+pos_id+edad+inm_prop_cas20_w+dif_inm+nation_t1+cuestion_mig"
h.ed.know.time <- "ola*educ*know_inm_t1t4+quintil1+ess+know_inm_t1t4+frien_inm_t1t4+pos_id+edad+inm_prop_cas20_w+dif_inm+nation_t1+cuestion_mig"
h.ed.fri.time <- "ola*educ*frien_inm_t1t4+quintil1+ess+know_inm_t1t4+frien_inm_t1t4+pos_id+edad+inm_prop_cas20_w+dif_inm+nation_t1+cuestion_mig"

hipotesis <- c(h1.cat,h1,h2.educ,h2.incom,h3,h4.know,h4.friend
               # h.ed.know.time,
               # h.ed.fri.time
               )
# Set the independent variables (IVs)
ivs<- df_study1 %>% select(starts_with("in_"),"conviviality","identity") %>% names()

@@

# Tables_______________________________________________________________________
omit <- "(pos_id)|(edad)|(cuestion_mig)|(nation_t1)|(quintil1QNA)|(Intercept)"
reorderc <- c(1:4,21,5:20,22:35) # the depends on the number of coeficients (!)
# detail for subsections:
# https://stackoverflow.com/questions/69338331/r-markdown-create-section-headers-in-r-and-print-r-output-in-same-section

cat(paste0("\n## ","Conviviality (avg)","\n"))

knitreg(l = fit1[names(fit1)[grepl("conviviality", names(fit1),"\n")]],
        omit.coef = omit,
        reorder.coef = reorderc
        )

cat(paste0("\n ","<br>","\n"))

cat(paste0("\n## ","Identity (avg)","\n"))

## Education dummy {-}

```{r average-primary, fig.dim=c(10,6), results='asis'}
rm(list=ls())
if (!require("pacman")) install.packages("pacman") # instalar pacman
                            # cargar librerias
pacman::p_load(dplyr,       # Manipulacion de datos
               knitr,
               kableExtra,
               summarytools,
               lme4,
               texreg,
               sjPlot
               )
load(file = here::here("input/data-proc/df_study_t5_ind_comunas.RData"))

old <- theme_set(theme_bw());theme_set(old)
theme_replace(legend.position="bottom")

# generate analytical sample
df_study1 <- 
  df_study_long_t5_comunas %>%
  select(idencuesta,ola,comuna,cuestion_mig,
         in_ansied,in_simpat,in_valfam,in_valami,in_amigcl,
         in_simili,in_amsimb,in_acpier,in_acadop,
         conviviality, identity,
         in_amreal,educ,quintil1:edad,
         inm_prop_cas17_w,inm_prop_cas20_w,dif_inm) %>% 
  na.omit() %>% 
  mutate(
         ola_f = ola,
         ola=as.numeric(ola),
         primary = car::recode(educ,recodes = "'Primary'=1;else=0",as.factor = T),
         -in_amreal
         )

# Hypothesis___________________________________________________________________
h1.cat <- "ola_f+primary+quintil1+ess+know_inm_t1t4+frien_inm_t1t4+pos_id+edad+inm_prop_cas20_w+dif_inm+nation_t1+cuestion_mig"
h1 <- "ola+primary+quintil1+ess+know_inm_t1t4+frien_inm_t1t4+pos_id+edad+inm_prop_cas20_w+dif_inm+nation_t1+cuestion_mig"
h2.primary <- "ola*primary+quintil1+ess+know_inm_t1t4+frien_inm_t1t4+pos_id+edad+inm_prop_cas20_w+dif_inm+nation_t1+cuestion_mig"
h2.incom <- "ola+primary+quintil1*ola+ess+know_inm_t1t4+frien_inm_t1t4+pos_id+edad+inm_prop_cas20_w+dif_inm+nation_t1+cuestion_mig"
h3 <- "ola*dif_inm+primary+quintil1+ess+know_inm_t1t4+frien_inm_t1t4+pos_id+edad+inm_prop_cas20_w+dif_inm+nation_t1+cuestion_mig"
h4.know <- "ola+dif_inm+primary+quintil1+ess+know_inm_t1t4*ola+frien_inm_t1t4+pos_id+edad+inm_prop_cas20_w+dif_inm+nation_t1+cuestion_mig"
h4.friend <- "ola+dif_inm+primary+quintil1+ess+know_inm_t1t4+frien_inm_t1t4*ola+pos_id+edad+inm_prop_cas20_w+dif_inm+nation_t1+cuestion_mig"
h.ed.know.time <- "ola*primary*know_inm_t1t4+quintil1+ess+know_inm_t1t4+frien_inm_t1t4+pos_id+edad+inm_prop_cas20_w+dif_inm+nation_t1+cuestion_mig"
h.ed.fri.time <- "ola*primary*frien_inm_t1t4+quintil1+ess+know_inm_t1t4+frien_inm_t1t4+pos_id+edad+inm_prop_cas20_w+dif_inm+nation_t1+cuestion_mig"
hipotesis <- c(h1.cat,h1,h2.primary,h2.incom,h3,h4.know,h4.friend,
               h.ed.know.time,
               h.ed.fri.time
               )
# Set the independent variables (IVs)
ivs<- df_study1 %>% select("in_amreal","conviviality","identity") %>% names()

# Tables_______________________________________________________________________
omit <- 
  paste0(
    "(pos_id)|(edad)|(cuestion_mig)|(nation_t1)|(quintil1QNA)|(Intercept)"
    )
reorderc <- c(1:4,19,5:18,20:43) # the depends on the number of coeficients (!)
# detail for subsections:
# https://stackoverflow.com/questions/69338331/r-markdown-create-section-headers-in-r-and-print-r-output-in-same-section

cat(paste0("\n## ","Conviviality (avg)","\n"))

knitreg(l = fit1[names(fit1)[grepl("conviviality", names(fit1),"\n")]],
        omit.coef = omit,
        single.row = F,
        reorder.coef = reorderc
        )

cat(paste0("\n## ","Identity (avg)","\n"))

knitreg(l = fit1[names(fit1)[grepl("identity", names(fit1),"\n")]],
        omit.coef = omit,
        reorder.coef = reorderc
        )

cat(paste0("\n## ","Unemployment increases (Threat)","\n"))

knitreg(l = fit1[names(fit1)[grepl("in_amreal", names(fit1),"\n")]],
        omit.coef = omit,
        reorder.coef = reorderc
        ) 
```

```{r by-item, fig.dim=c(10,6), results='asis'}
rm(list=ls())
if (!require("pacman")) install.packages("pacman") # instalar pacman
                            # cargar librerias
pacman::p_load(dplyr,       # Manipulacion de datos
               knitr,
               kableExtra,
               summarytools,
               lme4,
               texreg,
               sjPlot
               )
load(file = here::here("input/data-proc/df_study_t5_ind_comunas.RData"))

old <- theme_set(theme_bw());theme_set(old)
theme_replace(legend.position="bottom")

# generate analytical sample
df_study1 <- 
  df_study_long_t5_comunas %>%
  select(idencuesta,ola,comuna,cuestion_mig,
         in_ansied,in_simpat,in_valfam,in_valami,in_amigcl,
         in_simili,in_amsimb,in_acpier,in_acadop,
         conviviality, identity,
         in_amreal,educ,quintil1:edad,
         inm_prop_cas17_w,inm_prop_cas20_w,dif_inm) %>% 
  na.omit() %>% 
  mutate(
         ola_f = ola,
         ola=as.numeric(ola),
         primary = car::recode(educ,recodes = "'Primary'=1;else=0",as.factor = T),
         -in_amreal
         )

# Hypothesis___________________________________________________________________
h1.cat <- "ola_f+educ+quintil1+ess+know_inm_t1t4+frien_inm_t1t4+pos_id+edad+inm_prop_cas20_w+dif_inm+nation_t1+cuestion_mig"
h1 <- "ola+educ+quintil1+ess+know_inm_t1t4+frien_inm_t1t4+pos_id+edad+inm_prop_cas20_w+dif_inm+nation_t1+cuestion_mig"
h2.educ <- "ola*educ+quintil1+ess+know_inm_t1t4+frien_inm_t1t4+pos_id+edad+inm_prop_cas20_w+dif_inm+nation_t1+cuestion_mig"
h2.incom <- "ola+educ+quintil1*ola+ess+know_inm_t1t4+frien_inm_t1t4+pos_id+edad+inm_prop_cas20_w+dif_inm+nation_t1+cuestion_mig"
h3 <- "ola*dif_inm+educ+quintil1+ess+know_inm_t1t4+frien_inm_t1t4+pos_id+edad+inm_prop_cas20_w+dif_inm+nation_t1+cuestion_mig"
h4.know <- "ola+dif_inm+educ+quintil1+ess+know_inm_t1t4*ola+frien_inm_t1t4+pos_id+edad+inm_prop_cas20_w+dif_inm+nation_t1+cuestion_mig"
h4.friend <- "ola+dif_inm+educ+quintil1+ess+know_inm_t1t4+frien_inm_t1t4*ola+pos_id+edad+inm_prop_cas20_w+dif_inm+nation_t1+cuestion_mig"
h.ed.know.time <- "ola*educ*know_inm_t1t4+quintil1+ess+know_inm_t1t4+frien_inm_t1t4+pos_id+edad+inm_prop_cas20_w+dif_inm+nation_t1+cuestion_mig"
h.ed.fri.time <- "ola*educ*frien_inm_t1t4+quintil1+ess+know_inm_t1t4+frien_inm_t1t4+pos_id+edad+inm_prop_cas20_w+dif_inm+nation_t1+cuestion_mig"
hipotesis <- c(h1.cat,h1,h2.educ,h2.incom,h3,h4.know,h4.friend
               # h.ed.know.time,
               # h.ed.fri.time
               )
# Set the independent variables (IVs)
ivs<- df_study1 %>% select(
  starts_with("in_")
  # "conviviality",
  # "identity"
  ) %>% names()

# Tables_______________________________________________________________________
omit <- 
  paste0(
    "(pos_id)|(edad)|(cuestion_mig)|(nation_t1)|(quintil1QNA)|(Intercept)"
    )
reorderc <- c(1:4,21,5:20,22:35) # the depends on the number of coeficients (!)
# detail for subsections:
# https://stackoverflow.com/questions/69338331/r-markdown-create-section-headers-in-r-and-print-r-output-in-same-section

cat(paste0("\n# ","Annexes","\n"))

@@

knitreg(l = fit1[names(fit1)[grepl("in_ansied", names(fit1))]],
        omit.coef = omit,reorder.coef = reorderc
        )
cat(paste0("\n## ","B. Simpathy ","\n"))

@@

@@

knitreg(l = fit1[names(fit1)[grepl("in_acadop", names(fit1))]],
        omit.coef = omit,reorder.coef = reorderc)
```

### 2022-06-22 production/prod_prep.Rmd
modelos dummy educacion y 3-way-interac

know_inm_bi <- 
elsoc %>% group_by(idencuesta) %>%
  summarize(know_inm_bi_t4=know_inm_bi[ola==4],
            know_inm_bi_t1=know_inm_bi[ola==1],
            know_inm_t1t4 = know_inm_bi[ola==4] - know_inm_bi[ola==1]
            )

@@

elsoc$know_inm_t1t4 <- factor(elsoc$know_inm_t1t4,levels = c(-1,0,1),
                              labels = c("No longer know","Still know","Now know"))

elsoc$know_inm_t1t4 <- set_label(elsoc$know_inm_t1t4,
                                  label = "Know immigrants (diff. t4 - t1)")
sjmisc::frq(elsoc$know_inm_t1t4)
# sjPlot::tab_xtab(elsoc$know_inm_t1t4,elsoc$ola)

@@

frien_inm_bi <- 
elsoc %>% group_by(idencuesta) %>%
  summarize(frien_inm_bi_t4=frien_inm_bi[ola==4],
            frien_inm_bi_t1=frien_inm_bi[ola==1],
            frien_inm_t1t4 = frien_inm_bi[ola==4] - frien_inm_bi[ola==1]
            )

elsoc <- left_join(x = elsoc,y = frien_inm_bi, by = "idencuesta")
summary(elsoc$frien_inm_t1t4)
# if NA in difference, impute data from t4
elsoc$frien_inm_t1t4 <- if_else(condition = is.na(elsoc$frien_inm_t1t4),
                                true = elsoc$frien_inm_bi_t4,
                                false = elsoc$frien_inm_t1t4 )
summary(elsoc$frien_inm_t1t4)
# if NA in difference, impute data from t1
elsoc$frien_inm_t1t4 <- if_else(condition = is.na(elsoc$frien_inm_t1t4),
                                true = elsoc$frien_inm_bi_t1,
                                false = elsoc$frien_inm_t1t4)
sjmisc::frq(elsoc$frien_inm_t1t4)

elsoc$frien_inm_t1t4 <- factor(elsoc$frien_inm_t1t4,
                               levels = c(-1,0,1),
                               labels = c("No longer have","Still have","Now have"))

elsoc$frien_inm_t1t4 <- 
  set_label(elsoc$frien_inm_t1t4,
            label = "Have immigrant friends (diff. t4 - t1)")

sjmisc::frq(elsoc$frien_inm_t1t4)
# sjPlot::tab_xtab(elsoc$frien_inm_t1t4,elsoc$ola)

# Select variables______________________________________________________________
elsoc_long_2016_2021<- elsoc

>>>>

know_inm_bi <- 
elsoc %>% group_by(idencuesta) %>%
  summarize(know_inm_bi_t4=know_inm_bi[ola==4],
            know_inm_bi_t1=know_inm_bi[ola==1],
            # know_inm_t1t4 = know_inm_bi[ola==4] - know_inm_bi[ola==1],
            know_inm_t1t4 = paste0(know_inm_bi[ola==1],know_inm_bi[ola==4])
            )
sjmisc::frq(know_inm_bi$know_inm_t1t4)
know_inm_bi$know_inm_t1t4 <- 
  car::recode(know_inm_bi$know_inm_t1t4,
              recodes = "c('0NA','NA0','00')='Stable, do not know';c('1NA','NA1','11')='Stable, know';'01'='Now know';'10'='No longer know'",as.factor = T)

know_inm_bi$know_inm_t1t4 <- 
  factor(know_inm_bi$know_inm_t1t4,
         levels = c("Stable, do not know","Stable, know","Now know","No longer know"))
sjmisc::frq(know_inm_bi$know_inm_t1t4)

@@

elsoc$know_inm_t1t4 <- set_label(elsoc$know_inm_t1t4,
                                  label = "Know immigrants (diff. t4 - t1)")

sjmisc::frq(elsoc$know_inm_t1t4)
# sjPlot::tab_xtab(elsoc$know_inm_t1t4,elsoc$ola)

@@

frien_inm_bi <- 
elsoc %>% group_by(idencuesta) %>%
  summarize(frien_inm_bi_t4=frien_inm_bi[ola==4],
            frien_inm_bi_t1=frien_inm_bi[ola==1],
            # frien_inm_t1t4 = frien_inm_bi[ola==4] - frien_inm_bi[ola==1],
            frien_inm_t1t4 = paste0(frien_inm_bi[ola==1],frien_inm_bi[ola==4])
            )

sjmisc::frq(frien_inm_bi$frien_inm_t1t4)
frien_inm_bi$frien_inm_t1t4 <-
  car::recode(frien_inm_bi$frien_inm_t1t4,
              recodes = "c('0NA','NA0','00')='Stable, do not have friends';c('1NA','NA1','11')='Stable, have friends';'01'='Now have friends';'10'='No longer have friends';'NANA'=NA",as.factor = T)
sjmisc::frq(frien_inm_bi$frien_inm_t1t4)

frien_inm_bi$frien_inm_t1t4 <- 
  factor(frien_inm_bi$frien_inm_t1t4,
         levels = c("Stable, do not have friends","Stable, have friends",
                    "Now have friends","No longer have friends"))
sjmisc::frq(frien_inm_bi$frien_inm_t1t4)

elsoc <- left_join(x = elsoc,y = frien_inm_bi, by = "idencuesta")
sjmisc::frq(elsoc$frien_inm_t1t4)
# View(elsoc[c("idencuesta","frien_inm_bi_t4","frien_inm_bi_t1","frien_inm_t1t4")])

# # if NA in difference, impute data from t4
# elsoc$frien_inm_t1t4 <- if_else(condition = is.na(elsoc$frien_inm_t1t4),
#                                 true = elsoc$frien_inm_bi_t4,
#                                 false = elsoc$frien_inm_t1t4)
# summary(elsoc$frien_inm_t1t4)
# # if NA in difference, impute data from t1
# elsoc$frien_inm_t1t4 <- if_else(condition = is.na(elsoc$frien_inm_t1t4),
#                                 true = elsoc$frien_inm_bi_t1,
#                                 false = elsoc$frien_inm_t1t4)
sjmisc::frq(elsoc$frien_inm_t1t4)

# elsoc$frien_inm_t1t4 <- factor(elsoc$frien_inm_t1t4,
#                                levels = c(-1,0,1),
#                                labels = c("No longer have",
#                                           "Constant",
#                                           "Now have"))

# ref dejamos los 
elsoc$frien_inm_t1t4 <- 
  set_label(elsoc$frien_inm_t1t4,
            label = "Have immigrant friends (diff. t4 - t1)")

sjmisc::frq(elsoc$frien_inm_t1t4)
sjPlot::tab_xtab(elsoc$frien_inm_bi,elsoc$know_inm_bi)
# Select variables______________________________________________________________
elsoc_long_2016_2021<- elsoc
